---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# epifeatures

<!-- badges: start -->
<!-- badges: end -->

The objective of the epifueatures package is to provide the epidemiological characteristics of dengue transmission. The package is based on the work of Almeida et al. (2022). For a more detailed review, see Almeida IF, Lana RM, Codeco CT. 2022. How heterogeneous is the dengue transmission profile in Brazil? A study in six Brazilian states. PLOS Neglected Tropical Diseases.

## Installation

You can install the development version of epifeatures from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("fdzul/epifeatures")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(epifeatures)
## basic example code
```
