---
title: "Epidemiological Characteristics Without Cases"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(epifeatures)
```


[Almeida et al 2023 (Table 1)](https://journals.plos.org/plosntds/article?id=10.1371/journal.pntd.0010746) provide the epidemiological characteristics without cases Dc3, Dc6, Dsmax, & Dsmax.

| Epi-features | Abbreviation | Definition | Unit of measure | Serie | Value |
|---------|:-----:|:------:|:------:|:------:|:------:|
| Length of case-free period (transmission)  | Ds3   | Frequency of at least three consecutive weeks with no record of dengue cases during the epidemiological year. Unit of measure: dimensionless (count) |dimensionless (count) |[2,0,0,0,3,5,0,0,0,0,2]  |   2 |
|    | Ds6  | Frequency of at least six consecutive weeks with no record of dengue cases during the epidemiological year. |  dimensionless (count)   | [3,0,0,0,0,0,0,3,5,0,0,0,2] |  1 |
|    | Dsmax  | Maximum period of consecutive weeks within an epidemiological year with no record of dengue cases |  week  | NA |  NA |
|    | Dsmed  | Median length of a one-year epidemiological period with no record of dengue cases | week  | NA |  NA |


## Ds3 
```{r}
epifeatures::ef_woc(x = c(2, 0, 0, 0, 3, 5, 0, 0, 0, 0,2), 
                    dc_threshold = 0, 
                    c_weeks = 3, 
                    ef = "ds3")
```

```{r}
epifeatures::ef_woc(x = c(2, 0, 0, 0, 3, 5,2), 
                    dc_threshold = 0, 
                    c_weeks = 3, 
                    ef = "ds3")
```


```{r}
epifeatures::ef_woc(x = c(2, 0, 0, 0, 0, 0,0, 1), 
                    dc_threshold = 0, 
                    c_weeks = 3, 
                    ef = "ds3")
```




## Ds6 
```{r}
epifeatures::ef_woc(x = c(3,0,0,0,0,0,0,3,5,0,0,0,2), 
                    dc_threshold = 0, 
                    c_weeks = 6, 
                    ef = "ds6")
```


```{r}
epifeatures::ef_woc(x = c(3,0,0,0,0,0,0,3,5,0,0,0,2, 0,0,0,0,0,0), 
                    dc_threshold = 0, 
                    c_weeks = 6, 
                    ef = "ds6")
```


## Dsmax

```{r}
epifeatures::ef_woc(x = c(2, 0, 0, 0, 3, 5, 0, 0, 0, 0,2), 
                    dc_threshold = 0, 
                    c_weeks = 3, 
                    ef = "dsmax")
```

```{r}
epifeatures::ef_woc(x = c(2, 0, 0, 0,0,0,0, 3, 5, 0, 0, 0, 0,2), 
                    dc_threshold = 0, 
                    c_weeks = 6, 
                    ef = "dsmax")
```

## Dsmed
```{r}
epifeatures::ef_woc(x = c(2, 0, 0, 0, 3, 5, 0, 0, 0, 0,2), 
                    dc_threshold = 0, 
                    c_weeks = 3, 
                    ef = "dsmed")
```



